---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# finisterraR

<!-- badges: start -->

<!-- badges: end -->

finisterraR is an R API interface to access the FINISTERRA project
excavation data stored at data.finisterra.icarehb.com.

## Functions

| Function | Description | Returns |
|:---|:---|:---|
| `finisterra_server_connect()` | Authenticates with the API and creates a connection object. | `finisterra_con` |
<<<<<<< HEAD
| `get_site_data()` | Returns a joined dataframe of **XYZ** and **Context** tables for a specific site. | `data.frame` |
| `get_site_contexts()` | Retrieves the raw **Context** table for a specific site. | `data.frame` |
| `get_site_xyz()` | Retrieves the raw **XYZ** table for a specific site. | `data.frame` |
| `get_site_datums()` | Retrieves the **Datums** table for a specific site. | `data.frame` |
=======
| `get_site_data()` | Returns a joined dataframe of **XYZ** and **Context** records. | `data.frame` |
| `get_site_contexts()` | Fetches the raw **Context** table for a specific site. | `data.frame` |
| `get_site_xyz()` | Fetches the raw **XYZ** table for a specific site. | `data.frame` |
| `get_site_datums()` | Retrieves the **Datums** table. | `data.frame` |
>>>>>>> 06ef99d87408b5ee0f1a69d514a0e7eced1b162d
| `get_site_units()` | Retrieves the **Units** table for a specific site. | `data.frame` |
| `search_by_square()` | Joins and filters records for a specific excavation unit. | `data.frame` |

## Installation

You can install the development version of finisterraR like so:

``` r
devtools::install_github("cocoemily/finisterraR")
```

## Example

```{r example, eval = F}
library(finisterraR)

con <- finisterra_server_connect()
#enter username and password as prompted

esc <- get_site_data(con, "esc") 
gdc <- get_site_data(con, "gdc")

esc_datums <- get_site_datums(con, "esc")
gdc_datums <- get_site_datums(con, "gdc")
```
